High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-08-29 paper/main.tex
wrote some notes in the methods and discussion sections

\section*{Methods}
Our general approach to comprises four general steps.  First, we
derive a kernel-based approach to computing dynamic pairwise
correlations in a $T$ (timepoints) by $K$ (features) multivariate
timeseries, $\mathbf{X}_0$.  This yields a $T$ by $\mathcal{O}(K^2)$ matrix of
dynamic correlations, $\mathbf{Y}_1$, where each row comprises the upper
triangle of the correlation matrix at a single timepoint, reshaped
into a row vector (this reshaped vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a dimensionality reduction step
to project the matrix of dynamic correlations back onto a
$K$-dimensional space.  This yields a $T$ by $K$ matrix, $\mathbf{X}_1$, that
reflects an approximation of the dynamic correlations reflected in the
original data.  Third, we use repeated applications of the
kernel-based dynamic correlation step to $\mathbf{X}_n$ and the dimensionality
reduction step to the resulting $\mathbf{Y}_{n+1}$ to estimate high-order
dynamnic correlations.  Each application of these steps to a $T$ by
$K$ time series $\mathbf{X}_n$ yields a $T$ by $K$ matrix, $\mathbf{X}_{n+1}$, that
reflects the dynamic correlations between the columns of $\mathbf{X}_n$.  In
this way, we refer to $n$ as the \textit{order} of the timeseries,
where $\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$ denotes
$n^\mathrm{th}$-order dynamic correlations between the columns of
$\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding approach to
evaluate how well information contained in a given order (or weighted
mixture of orders) may be used to decode relevant cognitive states.
If including a given $\mathbf{X}_n$ in the feature set yields higher
classification accuracy on held-out data, we interpret this as
evidence that the given cognitive states are reflected in patterns of
$n^\mathrm{th}$-order correlations.

@@

Because $\mathbf{X}_n$ will have the same shape as the original data
$\mathbf{X}_0$, approximating $\mathbf{Y}_n$ with a lower-dimensional
$\mathbf{X}_n$ enables us to estimate high-order dynamic correlations
in a scalable way.  Given a $T$ by $K$ input matrix, the output of
Equation~\ref{eqn:timecorr} requires $\mathcal{O}(TK^2)$ space to
store.  Repeated applications of Equation~\ref{eqn:timecorr} (i.e.,
computing dynamic correlations between the columns of the outputted
dynamic correlation matrix) each require exponentially more space; in
general the $n^\mathrm{th}$-order dynamic correlations of a $T$ by $K$
timeseries occupies $\mathcal{O}(TK^{2n})$ space.  However, when we
approximate the output of Equation~\ref{eqn:timecorr} with a $T$ by
$K$ matrix (as described next), it becomes feasible to compute even
very high-order correlations in high-dimensional data.  Specifically,
approximating the $n^\mathrm{th}$-order dynamic correlations of a $T$
by $K$ timeseries requires only $\mathcal{O}(TK^2)$ space-- the same
as would be required to compute first-order dynamic
correlations. \textbf{JRM STOPPED HERE}

@@

Commonly used dimensionality reduction algorithms include Principal
Components Analysis~\citep[PCA; ][]{Pear01}, Probabilistic
PCA~\citep[PPCA; ][]{TippBish99}, Exploratory Factor
Analysis~\citep[EFA; ][]{Spea04}, Independent Components
Analysis~\citep[ICA; ][]{JuttHera91, ComoEtal91}, $t$-Stochastic
Neighbor Embedding~\citep[$t$-SNE; ][]{MaatHint08}, Uniform Manifold
Approximation and Projection~\citep[UMAP; ][]{McInHeal18},
non-negative matrix factorization~\citep[NMF; ][]{LeeSeun99},
Topographic Factor Analysis (TFA)~\cite{MannEtal14b}, Hierarchical
Topographic Factor analysis (HTFA)~\cite{MannEtal18}, Topographic
Latent Source Analysis (TLSA)~\cite{GersEtal11}, Dictionary
learning~\citep{MairEtal09a, MairEtal09b}, deep
autoencoders~\citep{HintSala06}, among others.  While complete
characterizations of each of these algorithms is beyond the scope of
the present manuscript, the general intuition driving these
approaches is to compute the $\hat{\mathbf{Y}}$ with $i$ columns that
is closest to the original $\mathbf{Y}$ with $j$ columns, and where
(typically) $i \ll j$.  The different approaches place different
constraints on what properties $\hat{\mathbf{Y}}$ must satisfy and
which aspects of the data are compared (and how) to characterize the
match between $\hat{\mathbf{Y}}$ and  $\mathbf{Y}$.

Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields a
$\hat{\mathbf{Y}}$ whose columns reflect weighted combinations (or
nonlinear transformations) of the original columns of $\mathbf{Y}$.
This has two main consequences.  First, with each repeated
dimensionality reduction, the resulting $\hat{\mathbf{Y}}_n$ has lower
and lower fidelity (with respect to what the ``true'' $\mathbf{Y}_n$
might have looked like without using dimensionality reduction to
maintain scalability).  In other words, computing $\hat{\mathbf{Y}}_n$
is a lossy operation.  Second, whereas the columns of $\mathbf{Y}_n$
may be mapped directly onto pairs of columns of $\mathbf{Y}_{n-1}$,
that mapping either becomes less cleanly defined in
$\hat{\mathbf{Y}}_n$ due to the reweightings and/or nonlinear
transformations.

\subsubsection*{Graph theoretic approaches to computing
  $\mathbf{X}_n$}

Graph theoretic measures take as input a matrix of interactions (e.g.,
using the above notation, an $F \times F$ correlation matrix or
binarized correlation matrix reconstituded from a single timepoint's
row of $\mathbf{Y}$) and return as output a set of $F$ measures
describing how each node (feature) sits within that interactions
matrix with respect to the rest of the population.  Common measures
include betweeness centrality~\citep[the proportion of shortest paths
between each pair of nodes in the population that involves the given
node in question; e.g., ][]{Newm05, OpsaEtal10, Bart04, GeisEtal08,
  Free77}; diversity and dissimilarity~\citep[characterizations of how
differently connected a given node is from others in the population;
e.g., ][]{Rao82, Lin09, RicoSzei06}; Eigenvector centrality and
pagerank centrality~\citep[measures of how influential a given node is
within the broader network; e.g., ][]{Newm08, Bona07, LohmEtal10,
  HaluEtal13}; transfer entropy and flow coefficients~\citep[a measure
of how much information is flowing from a given node to other nodes in
the network; e.g., ][]{HoneEtal07, Schr00}; $k$-coreness
centrality~\citep[a measure of the connectivity of a node within its
local sub-graph; e.g., ][]{AlvaEtal05, ChriFowl10}; within-module
degree~\citep[a measure of how many connections a node has to its
close neighbors in the network; e.g., ][]{RubiSpor10}; participation
coefficient~\citep[a measure of the diversity of a node's connections
to different sub-graphs in the network; e.g., ][]{RubiSpor10}; and
sub-graph centrality~\citep[a measure of a node's participation in all
of the network's sub-graphs; e.g., ][]{EstrRodr05}.

As an alternative to the above dimensionality reduction approach to
embedding $\mathbf{Y}_n$ in a lower-dimensional space, but still
allowing for scalable explorations of higher-order structure in the
data, we also explore using the above graph theoretic measures as a
means of obtaining $\hat{\mathbf{Y}}_n$.  In particular: for a given
graph theoretic measure, $\eta: \mathcal{R}^{F \times F} \rightarrow
\mathcal{R}^F$, we can use $\eta$ to tranform each row of
$\mathbf{Y}_n$ in a way that characterizes the corresponding
graph-theoretic properties of each column.  Whereas the dimensionality
reduction approach to computing $\hat{\mathbf{Y}}_n$ is lossy,
the graph-theory approach is lossless.  However, whereas the
dimensionality reduction approach maintains ties (direct or indirect)
to the original activity patterns reflected in $\mathbf{Y}_{n-1}$, the
graph-theory approach does not.  Instead, the graph-theory
characterizes the nature and timecourse of each feature's
\textit{participation} in the network.

\subsection*{Higher-order correlations}
Given a timeseries of dynamic correlations (e.g., obtained using
Eqn.~\ref{eqn:timecorr}), higher-order correlations reflect the
dynamic correlations between columns of $\mathbf{Y}$.  Given unlimited
computing resources, one could use repeated applications of
Equation~\ref{eqn:timecorr} to estimate these higher-order
correlations (i.e., substituting in the previous output, $\mathbf{Y}$,
for the input, $\mathbf{X}$ in the equation).  However, because each
output $\mathbf{Y}$ has $\mathcal{O}(F^2)$ columns relative to $F$ columns in
the input $\mathbf{X}$, the output of Equation~\ref{eqn:timecorr}
grows with the square of the number of repeated applications (total
cost of computing $n$\textsuperscript{th} order correlations is
$\mathcal{O}(F^{2n})$ for $n \in \mathcal{J}, n > 0$).  When $F$ or $n$ is large,
this approach quickly becomes intractable.

To make progress in computing $\mathbf{Y_{n+1}}$, we can approximate
$\mathbf{Y}_n$ by computing an $\mathcal{O}(F)$-dimensional embedding of
$\mathbf{Y}_n$, termed $\hat{\mathbf{Y}}_n$, and then we can apply
Equation~\ref{eqn:timecorr} to $\hat{\mathbf{Y}}_n$ rather than
directly to $\mathbf{Y}_n$.  This enables us to maintain $\mathcal{O}(n)$
scaling with respect to $n$, rather than exponential scaling via the
direct approach.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figs/methods_fig}
  \caption{\textbf{Computing higher order correlations. } Dynamic
    correlations
  are computed then approximated to the same size as original data
  using dimensionality reduction.
  This process is repeated, and can be used to compute up to any
  arbitrary order with compuations scaling linearly (as opposed to exponentially) with order. }
  \label{fig:methods_fig}
\end{figure}

There are many possible methods for computing $\hat{\mathbf{Y}}_n$
from $\mathbf{Y}_n$, including traditional dimensionality reduction
approaches and graph theory based approaches as described next.  In the
\textit{Discussion} section we elaborate on other potential approaches.

@@

@@

One challenge in studying dynamic interactions is the
computational resources required to calculate higher-order correlations. 
We developed a computationally tractable model of network dynamics (Fig.~\ref{fig:methods_fig}) that takes in a feature
timeseries and outputs approximated first-order dynamics (i.e.,
dynamic functional correlations), second-order dynamics
(reflecting homologous networks that dynamically form and disperse),
and higher-order network dynamics (up to tenth-order dynamic
correlations).

@@

How can we better understand how brain patterns change over
time? How can we quantify the potential network dynamics that might be
driving these changes? One way to judge the techniques of the future is
to look at the trajectory of the fMRI field so far has taken so far
(Fig.~\ref{fig:methods_fig}).  The field started with 
univariate activation, measuring the average activity for each voxel.
Analyses of multivariate activation followed, looking at spatial patterns of
activity over voxels. Next, correlations of activity were explored, first
with measures like resting connectivity that take temporal correlation
between a seed voxel and all other voxels then with full connectivty
that measure all pairwise correlations.  Additionally, this path of increasing
complexity also moved from static to dynamic measurements.  One
logical next step in this trajectory would be dynamic higher-order
correlations. We have created a method 
to support these calculations by scalably approximating dynamic higher-order
correlations.

>>>>

\section*{Methods}
Our general approach to comprises four general steps
(Fig.~\ref{fig:methods}).  First, we derive a kernel-based approach to
computing dynamic pairwise correlations in a $T$ (timepoints) by $K$
(features) multivariate timeseries, $\mathbf{X}_0$.  This yields a $T$
by $\mathcal{O}(K^2)$ matrix of dynamic correlations, $\mathbf{Y}_1$,
where each row comprises the upper triangle of the correlation matrix
at a single timepoint, reshaped into a row vector (this reshaped
vector is $(\frac{K^2 - K}{2})$-dimensional).  Second, we apply a
dimensionality reduction step to project the matrix of dynamic
correlations back onto a $K$-dimensional space.  This yields a $T$ by
$K$ matrix, $\mathbf{X}_1$, that reflects an approximation of the
dynamic correlations reflected in the original data.  Third, we use
repeated applications of the kernel-based dynamic correlation step to
$\mathbf{X}_n$ and the dimensionality reduction step to the resulting
$\mathbf{Y}_{n+1}$ to estimate high-order dynamnic correlations.  Each
application of these steps to a $T$ by $K$ time series $\mathbf{X}_n$
yields a $T$ by $K$ matrix, $\mathbf{X}_{n+1}$, that reflects the
dynamic correlations between the columns of $\mathbf{X}_n$.  In this
way, we refer to $n$ as the \textit{order} of the timeseries, where
$\mathbf{X}_0$ (order 0) denotes the original data and $\mathbf{X}_n$
denotes $n^\mathrm{th}$-order dynamic correlations between the columns
of $\mathbf{X}_0$.  Finally, we use a cross-validation--based decoding
approach to evaluate how well information contained in a given order
(or weighted mixture of orders) may be used to decode relevant
cognitive states.  If including a given $\mathbf{X}_n$ in the feature
set yields higher classification accuracy on held-out data, we
interpret this as evidence that the given cognitive states are
reflected in patterns of $n^\mathrm{th}$-order correlations.

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{figs/methods_fig}
  \caption{\textbf{Estimating dynamnic high-order correlations.}  Given
    a $T$ by $K$ matrix of multivariate timeseries data,
    $\mathbf{Y}_n$ (where $n \in \mathbb{N}, n \geq 0$), we use
    Equation~\ref{eqn:timecorr} to compute a timeseries of
    $K$ by $K$ correlation matrices, $\mathbf{Y}_{n+1}$.  We then
    approximate $\mathbf{Y}_{n+1}$ with the $T$ by $K$ matrix
    $\mathbf{X}_{n+1}$.  This process may be repeated to scalably estimate
    iteratively higher-order correlations in the data.}
  \label{fig:methods}
\end{figure}

@@

@@

The modern library of dimensionality reduction algorithms include
Principal Components Analysis~\citep[PCA; ][]{Pear01}, Probabilistic
PCA~\citep[PPCA; ][]{TippBish99}, Exploratory Factor
Analysis~\citep[EFA; ][]{Spea04}, Independent Components
Analysis~\citep[ICA; ][]{JuttHera91, ComoEtal91}, $t$-Stochastic
Neighbor Embedding~\citep[$t$-SNE; ][]{MaatHint08}, Uniform Manifold
Approximation and Projection~\citep[UMAP; ][]{McInHeal18},
non-negative matrix factorization~\citep[NMF; ][]{LeeSeun99},
Topographic Factor Analysis (TFA)~\cite{MannEtal14b}, Hierarchical
Topographic Factor analysis (HTFA)~\cite{MannEtal18}, Topographic
Latent Source Analysis (TLSA)~\cite{GersEtal11}, Dictionary
learning~\citep{MairEtal09a, MairEtal09b}, deep
autoencoders~\citep{HintSala06}, among others.  While complete
characterizations of each of these algorithms is beyond the scope of
the present manuscript, the general intuition driving these approaches
is to compute the $T$ by $I$ matrix, $\mathbf{X}$, that is closest
to the original $T$ by $J$ matrix, $\mathbf{Y}$, where (typically)
$I \ll J$.  The different approaches place different constraints on
what properties $\mathbf{X}$ must satisfy and which aspects of
the data are compared (and how) to characterize the match between
$\mathbf{X}$ and $\mathbf{Y}$.

Applying dimensionality reduction algorithms to $\mathbf{Y}$ yields a
$\mathbf{X}$ whose columns reflect weighted combinations (or nonlinear
transformations) of the original columns of $\mathbf{Y}$.  This has
two main consequences.  First, with each repeated dimensionality
reduction, the resulting $\mathbf{X}_n$ has lower and lower fidelity
(with respect to what the ``true'' $\mathbf{Y}_n$ might have looked
like without using dimensionality reduction to maintain scalability).
In other words, computing $\mathbf{X}_n$ is a lossy operation.
Second, whereas each columns of $\mathbf{Y}_n$ may always be mapped
directly onto specific pairs of columns of $\mathbf{Y}_{n-1}$, the
columns of $\mathbf{X}_n$ reflect weighted combinations and/or
nonlinear transformations of the columns of $\mathbf{Y}_n$.  Many
dimensionality reduction algorithms are invertable (or approximately
invertable).  However, attempting to map a given $\mathbf{X}_n$ back
onto the original feature space of $\mathbf{Y}_0$ will usually require
$\mathcal{O}(TK^{2n})$ space and therefore quickly becomes intractable
as $n$ or $K$ grow large.

\subsubsection*{Graph theoretic approaches to computing
  $\mathbf{X}_n$}
The above dimensionality reduction approaches to approximating a given
$\mathbf{Y}_n$ with a lower-dimensional $\mathbf{X}_n$ preserve a
(potentially recombined and transformed) mapping back to the original
data in $\mathbf{Y}_0$.  We also explore graph theoretic approaches
that forgo a preserved mapping back to the original data in favor of
preserving each feature's relative \textit{position} in the broader
network of interactions and connections.  To illustrate the
distinction between the two general approaches we explore, suppose a
network comprises nodes $A$, $B$, and $C$.  If $A$ and $B$ exhibit
uncorrelated activity patterns, the functional connection between
them will be (by definition) close to 0.  However, if $A$ and $B$ each
interact with $C$ in similar ways, we might attempt to capture those
similarities using a measure that reflects the how $A$ and $B$
interact in the network.

In general, graph theoretic measures take as input a matrix of
interactions (e.g., using the above notation, an $K$ by $K$
correlation matrix or binarized correlation matrix reconstituded from
a single timepoint's row of $\mathbf{Y}$) and return as output a set
of $K$ measures describing how each node (feature) sits within that
correlation matrix with respect to the rest of the population.  Widely
used measures include betweeness centrality~\citep[the proportion of
shortest paths between each pair of nodes in the population that
involves the given node in question; e.g., ][]{Newm05, OpsaEtal10,
  Bart04, GeisEtal08, Free77}; diversity and
dissimilarity~\citep[characterizations of how differently connected a
given node is from others in the population; e.g., ][]{Rao82, Lin09,
  RicoSzei06}; Eigenvector centrality and pagerank
centrality~\citep[measures of how influential a given node is within
the broader network; e.g., ][]{Newm08, Bona07, LohmEtal10,
  HaluEtal13}; transfer entropy and flow coefficients~\citep[a measure
of how much information is flowing from a given node to other nodes in
the network; e.g., ][]{HoneEtal07, Schr00}; $k$-coreness
centrality~\citep[a measure of the connectivity of a node within its
local sub-graph; e.g., ][]{AlvaEtal05, ChriFowl10}; within-module
degree~\citep[a measure of how many connections a node has to its
close neighbors in the network; e.g., ][]{RubiSpor10}; participation
coefficient~\citep[a measure of the diversity of a node's connections
to different sub-graphs in the network; e.g., ][]{RubiSpor10}; and
sub-graph centrality~\citep[a measure of a node's participation in all
of the network's sub-graphs; e.g., ][]{EstrRodr05}; among others.

For a given graph theoretic measure,
$\eta: \mathcal{R}^{K \times K} \rightarrow \mathbb{R}^K$, we can use
$\eta$ to tranform each row of $\mathbf{Y}_n$ in a way that
characterizes the corresponding graph-theoretic properties of each
column.  This results in a new $T$ by $K$ matrix, $\mathbf{X}_n$, that
reflects how the features reflected in the columns of $\mathbf{Y}_n$
participate in the network during each timepoint (row).

\subsection*{Higher-order correlations}

Because $\mathbf{X}_n$ has the same shape as the original data
$\mathbf{X}_0$, approximating $\mathbf{Y}_n$ with a lower-dimensional
$\mathbf{X}_n$ enables us to estimate high-order dynamic correlations
in a scalable way.  Given a $T$ by $K$ input matrix, the output of
Equation~\ref{eqn:timecorr} requires $\mathcal{O}(TK^2)$ space to
store.  Repeated applications of Equation~\ref{eqn:timecorr} (i.e.,
computing dynamic correlations between the columns of the outputted
dynamic correlation matrix) each require exponentially more space; in
general the $n^\mathrm{th}$-order dynamic correlations of a $T$ by $K$
timeseries occupies $\mathcal{O}(TK^{2n})$ space.  However, when we
approximate or summarize the output of Equation~\ref{eqn:timecorr} with a $T$ by
$K$ matrix (as described above), it becomes feasible to compute even
very high-order correlations in high-dimensional data.  Specifically,
approximating the $n^\mathrm{th}$-order dynamic correlations of a $T$
by $K$ timeseries requires only $\mathcal{O}(TK^2)$ additional space--
the same as would be required to compute first-order dynamic
correlations. In other words, the space required to store $n+1$
multivariate timeseries reflecting up to $n^\mathrm{th}$ order
correlations in the original data scales linearly with $n$ using our
approach (Fig.~\ref{fig:methods}). \textbf{JRM STOPPED HERE}

\subsection*{Data}
We examined two types of data: synthetic data and human functional
neuroimaging data.  We constructed and leveraged the synthetic data to
evaluate our general approach.  Specifically, we tested how well
Equation~\ref{eqn:timecorr} could be used to recover known dynamic
correlations using different choices of kernel ($\kappa$;
Fig.~\ref{fig:kernels}), for each of several synthetic datasets that
exhibited different temporal properties.  We applied our approach to a
functional neuroimaging dataset to test the hypothesis that ongoing
cognitive processing is reflected in high-order dynamic correlations.
We used an across-participant classification test to estimate whether
dynamic correlations of different orders contain information about
which timepoint in a story participants were listening to.

\subsubsection*{Synthetic data}
\paragraph*{Constant.}
\paragraph*{Random.}
\paragraph*{Ramping.}
\paragraph*{Event.}

\subsubsection*{Functional neuroimaging data collected during story
  listening}

\subsection*{Estimating high-order correlations in neuroimaging data}

\subsection*{Temporal decoding}
\subsubsection*{Forward inference, cross validation, and feature selection}
\subsubsection*{Identifying robust decoding results}
\subsubsection*{Reverse inference}

\textbf{JRM OUTLINE STOPPED HERE}

@@

\begin{itemize}
  \item Methods advances: kernel-based dynamic correlations, extension to
    dynamic ISFC, efficient method for estimating high-order dynamic
    correlations, identifying robust results by averaging
  \item Discoveries:
    \begin{itemize}
      \item Dimensionality reduction and graph theoretic approaches
        give different insights into the data and identify different
        patterns as being relevant to cognition (different peak
        orders).
        \item An insight common to both approaches is that high-order
          (greater than first order) dynamic correlations are
          informative about ongoing high-level cognitive processing.
          As the level of cognitive processing decreases, cognition is
          reflected by lower-order correlations.
        \item Correlations at different orders are also associated
          with different networks of brain regions.  However, which
          networks reflect which types of interactions depends on the
          current task.  In general, lower order correlations during
          auditory listening reflect processing of low-level
          (auditory) features; mid-order correlations reflect speech
          and linguistic processing; higher-order correlations reflect
          across-sensory integration (e.g. ties to visual areas) and
          cognitive control areas.  This hierarchy dissolves during
          lower-order cognitive processing.
      \end{itemize}
  \end{itemize}

@@

One challenge in studying dynamic interactions is the
computational resources required to calculate higher-order correlations. 
We developed a computationally tractable model of network dynamics (Fig.~\ref{fig:methods}) that takes in a feature
timeseries and outputs approximated first-order dynamics (i.e.,
dynamic functional correlations), second-order dynamics
(reflecting homologous networks that dynamically form and disperse),
and higher-order network dynamics (up to tenth-order dynamic
correlations).

@@

How can we better understand how brain patterns change over
time? How can we quantify the potential network dynamics that might be
driving these changes? One way to judge the techniques of the future is
to look at the trajectory of the fMRI field so far has taken so far
(Fig.~\ref{fig:methods}).  The field started with 
univariate activation, measuring the average activity for each voxel.
Analyses of multivariate activation followed, looking at spatial patterns of
activity over voxels. Next, correlations of activity were explored, first
with measures like resting connectivity that take temporal correlation
between a seed voxel and all other voxels then with full connectivty
that measure all pairwise correlations.  Additionally, this path of increasing
complexity also moved from static to dynamic measurements.  One
logical next step in this trajectory would be dynamic higher-order
correlations. We have created a method 
to support these calculations by scalably approximating dynamic higher-order
correlations.
